%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience \& Training}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Information Technology Engineer}
    {Ezz Al Dekheila Steel Co. (EZDK)}
    {Alexandria, Egypt}
    {Jul 2025}
    {
      \begin{cvitems}
        \item {Worked hands-on with Oracle E-Business Suite (EBS) and Oracle DB; wrote SQL scripts for data extraction, reporting, and routine data operations across production databases.}
        \item {Assisted in diagnosing and resolving infrastructure issues across the plant network; gained practical exposure to enterprise networking fundamentals, server configuration, and hardware troubleshooting in an industrial environment.}
      \end{cvitems}
    }

  \vspace{4mm}
%---------------------------------------------------------
  \cventry
    {Cyber Security Engineer}
    {Arabian Academy Security}
    {Alexandria, Egypt}
    {Jun 2024 -- Sep 2024}
    {
      \begin{cvitems}
        \item {Studied and applied GRC frameworks including ISO 27001, GDPR, and PCI-DSS; conducted risk assessments and contributed to security policy documentation.}
        \item {Hands-on practice with SIEM tools for log analysis and threat detection; performed penetration testing exercises using Kali Linux, Nmap, Burp Suite, and Metasploit; administered Active Directory environments.}
        \item {Explored threat intelligence workflows and incident response procedures in a structured training environment.}
      \end{cvitems}
    }

  \vspace{4mm}
%---------------------------------------------------------
  \cventry
    {Ethical Hacking --- Digital Egypt Youth Program}
    {National Institute for Telecommunication Education}
    {}
    {Nov 2025 -- Jan 2026}
    {
      \begin{cvitems}
        \item {72-hour certified course (score: \textbf{95\%}); covered reconnaissance, network scanning, vulnerability analysis, system \& web application security, SQL injection, DoS attacks, and basic cryptography.}
        \item {Reinforced practical offensive-security skills and deepened understanding of the full ethical hacking lifecycle — from footprinting through exploitation and reporting.}
      \end{cvitems}
    }

  \vspace{4mm}
%---------------------------------------------------------
  \cventry
    {Microsoft Full Stack Developer Professional Certificate}
    {Microsoft $\times$ Coursera}
    {}
    {Dec 2024}
    {
      \begin{cvitems}
        \item {Completed a structured curriculum covering full-stack development with React and Node.js, REST API design and integration, relational and NoSQL database management.}
        \item {Applied security best practices (authentication, authorization, input validation) and DevOps fundamentals including containerization, CI/CD pipelines, and deployment monitoring.}
      \end{cvitems}
    }

  \vspace{4mm}
%---------------------------------------------------------
  \cventry
    {Linux Administration (Admin I \& II)}
    {Information Technology Institute (ITI)}
    {}
    {Jul 2025}
    {
      \begin{cvitems}
        \item {Covered core Linux system administration: user and group management, file permissions, process control, and storage configuration (LVM, RAID, partitioning).}
        \item {Configured network interfaces, DNS, DHCP, and SSH; automated routine tasks with Bash shell scripting; practiced system monitoring and log analysis.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
