%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Courses \& Internships}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

% ----------------------------------------------------------------
  \cventry
    {Information Technology Engineer} % Job title/Position
    {Ezz Al Dekheila Steel Co. (EZDK)} % Organization
    {Alexandria, Egypt} % Location
    {Jul 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Gained hands-on experience with Oracle Database and ERP systems, working with Oracle E-Business Suite to manage enterprise data and processes.}
        \item {Studied networking fundamentals and troubleshooting for core infrastructure concepts.}
        \item {Developed and optimized database scripts using SQL to streamline data operations.}
      \end{cvitems}
    }
    
  \vspace{5mm}
% ----------------------------------------------------------------
  \cventry
    {Linux Administration} % Job title/Position
    {Information Technology Institute} % Organization
    {} % Location
    {Jul 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Training on Admin I and Admin II: hands-on experience in user/group management, file permissions, and process control.}
        \item {Practiced storage configuration, network setup, shell scripting, and basic server administration.}
      \end{cvitems}
    }
    
  \vspace{5mm}
% ----------------------------------------------------------------
  \cventry
    {Microsoft Full Stack Developer Professional Certificate} % Job title/Position
    {Microsoft x Coursera} % Organization
    {} % Location
    {Dec 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Covered full-stack development, database management (SQL/NoSQL), and API design.}
        \item {Learned security best practices, scalability and performance optimization, and DevOps techniques for deployment and monitoring.}
      \end{cvitems}
    }
    
  \vspace{5mm}
% -------------------------------------------------------
  \cventry
    {Google Cybersecurity Professional} % Job title/Position
    {Google x Coursera} % Organization
    {} % Location
    {Sep 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Covered cybersecurity fundamentals: risks, threats, vulnerabilities, and mitigation techniques.}
        \item {Gained practical experience with SIEM tools and skills in Python, Linux, and SQL.}
      \end{cvitems}
    }
    
  \vspace{5mm}
% -------------------------------------------------------
  \cventry
    {SQL Injection Attacks} % Job title/Position
    {EC-Council} % Organization
    {} % Location
    {Aug 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Learned about SQL injection attacks — how malicious SQL can be injected into input fields to manipulate databases — and mitigation strategies to protect applications and data.}
      \end{cvitems}
    }
    
  \vspace{5mm}
% -------------------------------------------------------
  \cventry
    {Computer Network Fundamentals} % Job title/Position
    {MaharaTech} % Organization
    {} % Location
    {Aug 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Covered computer network fundamentals and key components.}
        \item {Compared network topologies and categories, and reviewed OSI and TCP/IP models.}
      \end{cvitems}
    }
    
  \vspace{5mm}
% ----------------------------------------------------------------
  \cventry
    {CompTIA Security+} % Job title/Position
    {NetRiders Academy} % Organization
    {} % Location
    {Jul 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Studied attacks, threats and vulnerabilities, and architecture and design principles.}
        \item {Covered operations, incident response, and governance, risk, and compliance topics.}
      \end{cvitems}
    }
    
  \vspace{5mm}
% ----------------------------------------------------------------
  \cventry
    {ISC2 — Online (Self-paced)} % Job title/Position
    {ISC2} % Organization
    {} % Location
    {Jul 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Focused on security operations, cyber threat intelligence, and risk assessment.}
        \item {Studied network security, incident response, information security, and endpoint protection.}
        \item {Handled multiple dynamic roles and included a dashboard for system control.}
      \end{cvitems}
    }
    
  \vspace{5mm}
% ----------------------------------------------------------------
  \cventry
    {CEH v12} % Job title/Position
    {Skillsoft} % Organization
    {} % Location
    {Sep 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Cybersecurity concepts, attack methodologies, and information warfare.}
        \item {Implemented multiple roles (admin and user); admin can manage user roles.}
        \item {Project features authentication, cinema/showtime selection, and seat selection.}
      \end{cvitems}
    }

  \vspace{5mm}
% ----------------------------------------------------------------
  \cventry
    {CCNA v7} % Job title/Position
    {Cisco Networking Academy} % Organization
    {} % Location
    {Sep 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Introduction to networks, routing \& switching, enterprise networking, security, and automation.}
        \item {Hands-on experience with Cisco routers and switches, network configuration, and troubleshooting.}
        \item {Basic understanding of network protocols and services.}
      \end{cvitems}
    }

  \vspace{5mm}
% ----------------------------------------------------------------
  \cventry
    {Networking at ABC} % Job title/Position
    {Cisco, Microsoft} % Organization
    {} % Location
    {Dec 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {CCNA and MCSA fundamentals.}
        \item {Hands-on experience with routers, switches, and network configuration.}
        \item {Basic understanding of network protocols and troubleshooting techniques.}
      \end{cvitems}
    }

% ----------------------------------------------------------------
\end{cventries}